Exact Phylodynamics via Structured Markov Genealogy Processes

### 2024-02-12 ms.Rnw
update

<<prefix,include=FALSE,cache=FALSE,purl=FALSE>>=
prefix <- "sgp"
source("setup.R")
@
<<packages,include=FALSE,cache=FALSE>>=
library(tidyverse)
library(ggtree)
library(pomp)
library(cowplot)
library(viridis)
library(phylopomp)
stopifnot(getRversion() >= "4.3")
stopifnot(packageVersion("pomp")>="5.1")
stopifnot(packageVersion("phylopomp")>="0.10.1")
theme_set(theme_bw(base_family="serif"))
set.seed(1159254136)
@

@@

\begin{figure}
  <<upo,fig.dim=c(6,8),out.width="60%",results="hide">>=
  freeze(
    seed=522390503,
    simulate(
      "SEIR",
      Beta=1,sigma=0.5,gamma=0.1,psi=0.4,delta=0.1,
      S0=10,E0=1,I0=1,R0=0,
      time=10
    )
  ) -> x

>>>>

<<prefix,include=FALSE,cache=FALSE,purl=FALSE>>=
prefix <- "sgp"
source("setup.R")
@
<<packages,include=FALSE,cache=FALSE>>=
library(tidyverse)
library(ggtree)
library(pomp)
library(cowplot)
library(viridis)
library(phylopomp)
stopifnot(getRversion() >= "4.3")
stopifnot(packageVersion("pomp")>="5.1")
stopifnot(packageVersion("phylopomp")>="0.10.2")
theme_set(theme_bw(base_family="serif"))
set.seed(1159254136)
@

@@

\begin{figure}
  <<upo,fig.dim=c(6,8),out.width="60%",results="hide">>=
  freeze(
    seed=522390503,
    simulate(
      "SEIR",
      Beta=1,sigma=0.5,gamma=0.1,psi=0.4,omega=0.1,
      S0=10,E0=1,I0=1,R0=0,
      time=10
    )
  ) -> x
